---
title: "text_as_data_assignment_1"
author: "Andrew Wells"
date: "10/6/2022"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

#Loading packages
library(pacman)
p_load(tidyverse, rvest, quanteda, quanteda.textstats, patchwork, xml2, XML)
```

## Scraping/getting text

```{r echo=TRUE, include=TRUE}
url <- "https://www.gutenberg.org/cache/epub/1934/pg1934.txt"
text <- read_html(url) %>%
  html_nodes("p") %>%
  html_text()
```

## Parsing text

I had trouble working with Regex, so tried this (very messy) work around to acquire the data and put it in the proper dataframe. 

```{r echo=TRUE, include=TRUE}
lines <- str_split(text, "\r\n")[[1]] #Extract all lines from website
lines <- str_trim(lines) #Remove spaces before text
df_lines <- as.data.frame(lines) #Create df with all lines from website as a row
df_lines <- df_lines[-(1:105), , drop = FALSE] #Clean unnecessary rows
df_lines <- head(df_lines,-352) #Clean unnecessary rows
rownames(df_lines) = seq(length=nrow(df_lines)) #Re-setting sequencing numbers in df

df_lines$temp_poem <- gsub("[a-z ][a-z ]+", "", df_lines$lines) #Creating new column with poem and book names

df <- df_lines %>% #Cleaning data so only poem and book names are in column
  mutate(temp_poem2 = case_when(
    lines == temp_poem ~ temp_poem,
    lines != temp_poem ~ " "
    )) %>%
  select(-c(temp_poem)) %>% #Remove "messy" poem column
  na_if("") %>% #Fill blank rows with NAs
  na_if(" ") %>%
  fill(temp_poem2, .direction = "downup") %>% #Fill in poem titles
  mutate(poem_title = case_when(
    lines == temp_poem2 ~ "NA",
    lines != temp_poem2 ~ temp_poem2)) %>%
  mutate(book_title = ifelse(lines %in% "SONGS OF INNOCENCE", "Songs of Innocence",
                       ifelse(lines %in% "SONGS OF EXPERIENCE", "Songs of Experience",
                              NA))) %>% #Filling in book titles
  fill(book_title, .direction = "downup")

df <- df[-(1:8), , drop = FALSE] #Dropping first unnecessary rows

df <- df %>%
  mutate(stan_1 = ifelse(grepl("[a-z]", lines), 0, 1)) %>% #Create column that identifies new stanzas
  fill(poem_title, .direction = "downup") %>% #Completely fill poems
  select(-c(temp_poem2)) %>% #Remove unnecessary poem column
  group_by(poem_title) %>%
  mutate(stan_2 = cumsum(ifelse(is.na(stan_1), 0, stan_1))) %>% #Creating a column that adds stanzas
  mutate(stan_n = stan_2 + 1) %>% #Index stanza column
  drop_na(lines) %>% #Drop NAs
  filter(poem_title != "NA") %>% #Drop NAs
  group_by(poem_title) %>% 
  mutate(line_n = row_number()) %>% #Create line number column
  select(-c(stan_1, stan_2)) #Remove unnecessary stanza columns

#Reordering columns
col_order <- c("line_n", "lines", "stan_n",
               "poem_title", "book_title")
df <- df[, col_order]

df
```

## Histogram for lines per poem

```{r echo=TRUE, include=TRUE}
df %>%
  group_by(poem_title) %>%
  summarise(lines_numbers = max(line_n)) %>% #Find the number of lines in each poem
  ggplot(aes(x=lines_numbers)) + geom_histogram(binwidth=1) + #Create plot with lines by number of poems
  labs(title= "Density of line counts in poems",
        x ="Number of lines", y = "Count") +
  theme_minimal()
```

## Document feature matrix: lines

```{r echo=TRUE, include=TRUE}
df$lines %>%
  tokens(remove_punc=TRUE) %>%
  tokens_remove(pattern=stopwords("en")) %>%
  tokens_wordstem("english") %>%
  dfm()
```

## Document feature matrix: poems

```{r echo=TRUE, include=TRUE}
df$poem_title %>%
  tokens(remove_punc=TRUE) %>%
  tokens_remove(pattern=stopwords("en")) %>%
  tokens_wordstem("english") %>%
  dfm()
```

## Plot comparing frequency of words in each book

```{r echo=TRUE, include=TRUE}
df_soi <- df %>%
  filter(book_title == "Songs of Innocence") #Filter for "Song of Innocence"

df_soe <- df %>%
  filter(book_title == "Songs of Experience") #Filter for "Song of Experience"

dfmat_soi <- df_soi$lines %>% #Document feature matrix for words from SoI
  tokens(remove_punc=TRUE) %>%
  tokens_remove(pattern=stopwords("en")) %>%
  tokens_wordstem("english") %>%
  dfm()

dfmat_soe <- df_soe$lines %>% #Document feature matrix for words from SoE
  tokens(remove_punc=TRUE) %>%
  tokens_remove(pattern=stopwords("en")) %>%
  tokens_wordstem("english") %>%
  dfm()

tfreq_soi <- dfmat_soi %>% 
  textstat_frequency() %>% head(20)
tfreq_soi$feature <- factor(tfreq_soi$feature, levels=tfreq_soi$feature)

tfreq_soe <- dfmat_soe %>% 
  textstat_frequency() %>% head(20)
tfreq_soe$feature <- factor(tfreq_soe$feature, levels=tfreq_soe$feature)

p1 <- ggplot(tfreq_soi, aes(x=frequency, y=feature)) + #Plot of word frequency in SoI
  geom_col() + theme_minimal() + labs(title= "Most frequent words in \n'Songs of Innocence'", x ="Frequency", y = "Feature")

p2 <- ggplot(tfreq_soe, aes(x=frequency, y=feature)) + #Plot of word frequency in SoE
  geom_col() + theme_minimal() + labs(title= "Most frequent words in \n'Songs of Experience'", x ="Frequency", y = "Feature")   

plot <- p1 + p2 #Combining plots
 
plot
```

The figures above represent the the 20 most used words in the books of poems "Songs of Innocence" and "Songs of Experience" by William Blake. Words that are more youthful and hopeful, such as: infant, child, happi(for happy or happiness), laugh, joy, sweet and littl(e) seem to feature more in "Songs of Innocence". The book "Songs of Experience" does feature the words joy, sweet and littl(e) in its 20 most common words, but these are all featured less than in "Songs of Innocence". The 20 most frequent words in "Songs of Experience" have a darker and arguably more mature tone. These words include: heart, morn, fear, weep, love and night. Interestingly, the words father and mother are both in the 20 most frequent words in "Songs of Experience", while the word mother is absent from the 20 most frequent in "Songs on Innocence". 

## Parsing XML text data

```{r echo=TRUE, include=TRUE}
data <- read_html("https://www.bundestag.de/resource/blob/915286/b3575a3167ddebf1cf988059be7614f6/20059-data.xml") #Acquiring link

vorname <- data %>% html_elements("vorname") #Extracting first names of politicians
df_vorname <- as_tibble(do.call(rbind, html_attrs(vorname)))
df_vorname$vorname <- vorname %>% html_text()

nachname <- data %>% html_elements("nachname") #Extracting last names of politicians
df_nachname <- as_tibble(do.call(rbind, html_attrs(nachname)))
df_nachname$nachname <- nachname %>% html_text()

namen <- bind_cols(df_vorname, df_nachname)
namen
```

## Parsing XML text data

```{r echo=TRUE, include=TRUE}
redner <- data %>% #Getting elements for speeches
  html_elements("p[klasse!=redner]") %>%
  html_text2()

df_parl <- as.data.frame(redner)

db <- df_parl %>%
  filter(grepl('Dietmar Bartsch', redner)) #Finding mentions of Dr. Dietmar Bartsch (die Linke)

db
```

## Using regular expressions

```{r echo=TRUE, include=TRUE}
kohle <- df_parl %>%
  filter(grepl('kohle|Kohle', redner)) #Finding speeches mentioning coal

kohle
```

There are 11 speeches containing either kohle or Kohle (coal). 
